---
output: html_document
---

# Part 1

```{r}
library(tidyverse)
```

1
```{r}
study_weights <- read_csv("data/SCOOPS datasets - study_weights.csv")
```

2
```{r}
empty_trays <- read_csv("data/SCOOPS datasets - empty_trays.csv")
weights_trays <- study_weights |>
  left_join(empty_trays, by = c("before_type" = "type"))
```

3
```{r}
weights_adjusted <- weights_trays |>
  mutate(before_adjusted = if_else(before_deducted, before_weight,
                                   before_weight - empty_weight),
         before_total = before_number * before_adjusted)
```

4
```{r}
weights_totaled <- weights_adjusted |>
  mutate(after_total = after_full_number * before_adjusted + after_partial_weights_total,
         weight_delta = before_total - after_total)
```

5
```{r}
weights_summary <- weights_totaled |>
  group_by(source, condition, week, day, meal, station, meat_type) |>
  summarise(weight_delta = sum(weight_delta, na.rm = TRUE)) |>
  ungroup()
```

6
```{r}
pilot_weights <- read_csv("data/SCOOPS datasets - pilot_weights.csv")
weights_combined <- weights_summary |> bind_rows(pilot_weights)
```

8
```{r}
weights_target <- weights_combined |>
  filter(station == "target", meal == "lunch")

weights_nontarget <- weights_combined |>
  filter(station == "non_target", meal == "dinner")

weights_total <- weights_combined |>
  filter(meal == "dinner") |>
  group_by(source, condition, week, day) |>
  summarise(weight_delta = sum(weight_delta), n = n()) |>
  ungroup()
```

9
```{r}
weights_target |> count(condition)
weights_nontarget |> count(condition)
weights_total |> count(condition)
```

debugging totals
```{r}
weights_combined |>
  filter(station == "target") |>
  count(condition)
# 27, 16 / 11
# melissa's numbers are right but should be filtered to lunch

weights_combined |>
  filter(station != "target") |>
  count(condition)
#  21, 12 / 9

weights_combined |>
  group_by(source, condition, week, day, meal, meat_type) |>
  filter(n() < 2)
```

instructions:
target: 31, 17 control / 14 intervention
total: 17, 12 control / 9 intervention

melissa:
target: 27, 16 control / 11 intervention
total: 31, 17 control / 14 intervention


# Part 2

Main comparison of interest: condition vs. intervention for intervention target (Cardinal Sage at lunch).
```{r}
ggplot(weights_target, aes(x = condition, y = weight_delta)) +
  geom_text(aes(label = day, colour = source), size = 2,
            position = position_dodge(width = 0.2)) +
  stat_summary(geom = "crossbar", width = 0.4)
```

Second comparison of interest: spillover effects, i.e. total at dinner.
```{r}
ggplot(weights_total, aes(x = condition, y = weight_delta)) +
  geom_text(aes(label = day), size = 2,
            position = position_dodge(width = 0.2)) +
  stat_summary(geom = "crossbar", width = 0.4)
```

# Part 3

Main comparison
```{r}
m1 <- lm(weight_delta ~ condition + source, weights_target)
summary(m1)
```

Spillover effects
```{r}
m2 <- lm(weight_delta ~ condition, weights_total)
summary(m2)
```

```{r}
f1 <- augment(m1, newdata = weights_target |> distinct(condition, source),
              interval = "confidence")

ggplot(weights_target, aes(x = condition, y = weight_delta)) +
  geom_text(aes(label = day, colour = source), size = 2,
            position = position_dodge(width = 0.2)) +
  geom_pointrange(aes(y = .fitted, ymin = .lower, ymax = .upper), data = f1)


f2 <- augment(m2, newdata = weights_nontarget |> distinct(condition),
              interval = "confidence")
ggplot(weights_total, aes(x = condition, y = weight_delta)) +
  geom_text(aes(label = day), size = 2,
            position = position_dodge(width = 0.2)) +
  geom_pointrange(aes(y = .fitted, ymin = .lower, ymax = .upper), data = f2)
```
