---
title: "SCOOPS survey data analysis"
output:
  html_document:
    highlight_downlit: yes
    theme: cosmo
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggthemes)
library(ggforce)
library(glue)
library(lubridate)
library(broom)

options(digits = 2)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE,
                      rows.print = 25)
.font <- "Source Sans Pro"
theme_set(theme_bw(base_family = .font))
theme_update(panel.grid = ggplot2::element_blank(),
             strip.background = ggplot2::element_blank(),
             legend.key = ggplot2::element_blank(),
             panel.border = ggplot2::element_blank(),
             axis.line = ggplot2::element_line(),
             strip.text = ggplot2::element_text(face = "bold"))
```

## Load and tidy data

```{r, echo=FALSE, eval=FALSE}
read_csv("private/SCOOPS_qualtrics.csv") |>
  select(-IPAddress, -email, -LocationLatitude, -LocationLongitude) |>
  write_csv("data/SCOOPS_qualtrics_sanitized.csv")
```

```{r}
start_date <- ymd("2022-10-03")
end_date <- ymd("2022-10-21")
conditions <- tibble(date = seq(start_date, end_date, by = "days")) |>
  filter(wday(date, week_start = 1) <= 5) |>
  mutate(condition = rep(c("control", "intervention"), each = 5, length.out = n()),
         condition = as_factor(condition),
         week = rep(1:6, each = 5, length.out = n()))

survey_raw <- read_csv("data/SCOOPS_qualtrics_sanitized.csv")

survey <- survey_raw |>
  slice(3:n()) |> # first two rows are qualtrics metadata
  filter(Finished == "True") |> # remove empty responses
  rename(recorded = RecordedDate) |> # keep relevant metadata cols
  select(matches("^[a-z]", ignore.case = FALSE)) |> # remove other metadata cols
  select(-feedback) |> # also remove
  rename(satisfaction = satisfaction_1, hunger = hunger_1, fullness = fullness_1) |> # sliders have funky column names
  mutate(across(c(satisfaction, hunger, fullness), as.integer)) |> # slider values are integers
  mutate(target = target == "Yes", meat_inclusion = meat_inclusion == "Yes") |> # yes/no values are true/false
  mutate(recorded = as_datetime(recorded), date = date(recorded),
         day = wday(date, label = TRUE), hour = hour(recorded),
         .after = recorded) |> # get useful components of datetime
  mutate(in_range = date >= start_date & date <= end_date &
         !(day %in% c("Sat", "Sun")) & hour >= 11 & hour < 16) |> # code responses from outside of study range
  left_join(conditions) |> # code conditions
  mutate(id = 1:n()) |>
  select(condition, week, everything())
```

## Response counts

Responses from outside of study range (before start, on weekend, or too late in the day): `r survey |> filter(!in_range) |> nrow()`

Responses from not eating at Cardinal Sage: `r survey |> filter(!target) |> nrow()`

Remaining responses: `r survey |> filter(target, in_range) |> nrow()`

Number of responses from each day:
```{r}
survey_filtered <- survey |> filter(target, in_range)
survey_filtered |> count(date, condition)
```

## Demographic breakdown

Diet information

```{r}
bind_rows(
  survey_filtered |> count(diet) |> rename(value = diet) |> mutate(category = "diet"),
  survey_filtered |> count(meat_freq) |> rename(value = meat_freq) |> mutate(category = "meat_freq"),
  survey_filtered |> count(fish_freq) |> rename(value = fish_freq) |> mutate(category = "fish_freq"),
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```

Demographic information

```{r}
bind_rows(
  survey_filtered |> count(stanford_status) |> rename(value = stanford_status) |> mutate(category = "stanford_status"),
  survey_filtered |> count(gender) |> rename(value = gender) |> mutate(category = "gender"),
  survey_filtered |> count(race) |> rename(value = race) |> mutate(category = "race")
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```


## Plot responses

Plot values by week:

```{r, fig.width=8, fig.height=4.5}
survey_long <- survey_filtered |>
  pivot_longer(c(satisfaction, hunger, fullness), names_to = "measure", values_to = "value") |>
  mutate(measure = fct_rev(measure))

ggplot(survey_long, aes(x = week, y = value, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  stat_summary(fun = mean, geom = "crossbar") +
  scale_x_continuous(labels = \(b) paste("Week", b)) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

## Models

### Meat inclusion independence check

Check if intervention is affecting whether meat was eaten:
```{r}
meat_inclusion_model <- lm(meat_inclusion ~ condition, data = survey_filtered)
summary(meat_inclusion_model)
augment(meat_inclusion_model, newdata = survey_filtered |> distinct(condition))
```

__Seems like a higher proportion of respondents are eating meat in intervention than control.__

### By condition

```{r}
contrasts(survey_long$condition) <- contr.sum

model_fun <- \(d) lm(value ~ condition, data = d)
coef_fun <- \(m) tidy(m, conf.int = TRUE) |> mutate(p.value = sprintf("%.2f", round(p.value, 2)))
fits_fun <- \(m) augment(m, se_fit = TRUE, interval = "confidence",
                         newdata = survey_long |> distinct(condition))

survey_fits <- survey_long |>
  nest(data = -measure) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun))
```

Differences by condition:
```{r}
survey_fits |>
  select(measure, coefs) |>
  unnest(coefs)

survey_fits |>
  select(measure, fits) |>
  unnest(fits)
```

```{r, echo=FALSE}
hunger_fits <- survey_fits |>
  select(measure, fits) |>
  unnest(fits) |>
  filter(measure == "hunger")
hungers <- set_names(hunger_fits$.fitted, hunger_fits$condition)
hunger_increase <- hungers[["intervention"]] - hungers[["control"]] / hungers[["control"]]
```

__No effect for satisfaction or fullness, respondents are `r hunger_increase`% more hungry in intervention that in control.__

Plot responses by condition with CIs from above models:
```{r, fig.width=8, fig.height=4.5}
fits <- survey_fits |> select(measure, fits) |> unnest(fits)
ggplot(survey_long, aes(x = condition, y = value, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                data = fits) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

### By condition x meat_inclusion

Now split up by whether meat was included:
```{r}
survey_fits_meat <- survey_long |>
  nest(data = -c(measure, meat_inclusion)) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun))
```

Differences by condition and whether meat was included:
```{r}
survey_fits_meat |>
  select(measure, meat_inclusion, coefs) |>
  unnest(coefs)

survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits)
```

__No effects for satisfaction or fullness for both groups.__

```{r, echo=FALSE}
hunger_fits_meat <- survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits) |>
  filter(measure == "hunger", meat_inclusion == "TRUE")
hungers_meat <- set_names(hunger_fits_meat$.fitted, hunger_fits_meat$condition)
hunger_increase_meat <- hungers_meat[["intervention"]] - hungers_meat[["control"]] / hungers_meat[["control"]]
```

__Hunger effect is coming from respondents who did not eat meat, they are `r hunger_increase_meat`% more hungry in intervention that in control.__

Plot responses by condition and meat inclusion with CIs from above models:
```{r, fig.width=10, fig.height=4.5}
fits_meat <- survey_fits_meat |> select(measure, meat_inclusion, fits) |> unnest(fits) |>
  mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))
survey_long <- survey_long |>
  mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))

ggplot(survey_long, aes(x = condition, y = value, color = condition)) +
  facet_wrap(vars(measure, meat_inclusion), nrow = 1) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                position = position_dodge(),
                data = fits_meat) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```
