---
title: "SCOOPS survey data analysis"
output:
  html_document:
    highlight_downlit: yes
    theme: cosmo
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggthemes)
library(ggforce)
library(glue)
library(lubridate)
library(broom)
library(ggh4x)

options(digits = 2)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE,
                      rows.print = 25, dev.args = list(png = list(type = "cairo")))
.font <- "Source Sans Pro"
theme_set(theme_bw(base_family = .font, base_size = 13))
theme_update(panel.grid = ggplot2::element_blank(),
             strip.background = ggplot2::element_blank(),
             legend.key = ggplot2::element_blank(),
             panel.border = ggplot2::element_blank(),
             axis.line = ggplot2::element_line(),
             strip.text = ggplot2::element_text(face = "bold"))
```

## Load and tidy data

```{r, echo=FALSE, eval=FALSE}
read_csv(glue("private/SCOOPS_qualtrics_{today()}.csv")) |>
  select(-IPAddress, -email, -LocationLatitude, -LocationLongitude) |>
  write_csv(glue("data/SCOOPS_qualtrics_sanitized_{today()}.csv"))
```

```{r}
survey_raw <- read_csv(glue("data/SCOOPS_qualtrics_sanitized_{today()}.csv"))

# code the condition of each day
start_date <- ymd("2022-10-03")
end_date <- ymd("2022-10-28")
conditions <- tibble(date = seq(start_date, end_date, by = "days")) |>
  filter(wday(date, week_start = 1) <= 5) |>
  mutate(condition = rep(c("control", "intervention"), each = 5, length.out = n()),
         condition = as_factor(condition),
         week = rep(1:6, each = 5, length.out = n()))

survey_tidy <- survey_raw |>
  slice(3:n()) |> # first two rows are qualtrics metadata
  filter(Finished == "True") |> # remove empty responses
  rename(recorded = RecordedDate) |> # keep relevant metadata cols
  select(matches("^[a-z]", ignore.case = FALSE)) |> # remove other metadata cols
  select(-feedback) |> # also remove
  rename(satisfaction = satisfaction_1, hunger = hunger_1, fullness = fullness_1) |> # sliders have funky column names
  mutate(across(c(satisfaction, hunger, fullness), as.integer)) |> # slider values are integers
  mutate(target = target == "Yes", meat_inclusion = meat_inclusion == "Yes") |> # yes/no values are true/false
  mutate(recorded = as_datetime(recorded), date = date(recorded),
         day = wday(date, label = TRUE), hour = hour(recorded),
         .after = recorded) |> # get useful components of datetime
  mutate(in_range = date >= start_date & date <= end_date &
         !(day %in% c("Sat", "Sun")) & hour >= 11 & hour <= 16) |> # code responses from outside of study range
  left_join(conditions) |> # code conditions
  mutate(id = 1:n()) |>
  select(condition, week, everything())
```

```{r}
# add in meat types from weight data
# weights_tidy <- read_rds("../data/weights_tidy.rds")
# day_meats <- weights_tidy |>
#   filter(meal == "lunch", !is.na(dish)) |>
#   distinct(monthday, station, dish) |>
#   mutate(station = fct_recode(station, target = "Cardinal Sage", other = "Core Menu"),
#          dish = str_to_lower(dish),
#          date = date(monthday)) |>
#   select(-monthday) |>
#   pivot_wider(names_from = station, values_from = dish, names_prefix = "meat_")
day_meats <- read_csv("data/day_meats.csv") |> select(date, meat_target)

survey <- survey_tidy |>
  left_join(day_meats, by = "date") |>
  mutate(across(where(is.character), as_factor))
```

## Response counts

Responses from outside of study range (before start, on weekend, or too late in the day): `r survey |> filter(!in_range) |> nrow()`

Responses from not eating at Cardinal Sage: `r survey |> filter(!target) |> nrow()`

Remaining responses: `r survey |> filter(target, in_range) |> nrow()`

Number of responses from each day:
```{r}
survey_filtered <- survey |> filter(target, in_range)
survey_filtered |> count(date, condition)
```

## Demographic breakdown

Diet information

```{r}
bind_rows(
  survey_filtered |> count(diet) |> rename(value = diet) |> mutate(category = "diet"),
  survey_filtered |> count(meat_freq) |> rename(value = meat_freq) |> mutate(category = "meat_freq"),
  survey_filtered |> count(fish_freq) |> rename(value = fish_freq) |> mutate(category = "fish_freq"),
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```

Demographic information

```{r}
bind_rows(
  survey_filtered |> count(stanford_status) |> rename(value = stanford_status) |> mutate(category = "stanford_status"),
  survey_filtered |> count(gender) |> rename(value = gender) |> mutate(category = "gender"),
  survey_filtered |> count(race) |> rename(value = race) |> mutate(category = "race")
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```


## Plot responses

Plot values by week:

```{r, fig.width=10, fig.height=4.5}
survey_long <- survey_filtered |>
  pivot_longer(c(satisfaction, hunger, fullness), names_to = "measure", values_to = "value") |>
  mutate(measure = fct_rev(measure))

ggplot(survey_long, aes(x = week, y = value, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  stat_summary(fun = mean, geom = "crossbar") +
  scale_x_continuous(labels = \(b) paste("Week", b)) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

## Models

### Meat inclusion independence check

Check if intervention is affecting whether meat was eaten:
```{r}
meat_inclusion_model <- lm(meat_inclusion ~ condition, data = survey_filtered)
summary(meat_inclusion_model)
augment(meat_inclusion_model, se_fit = TRUE, interval = "confidence",
        newdata = survey_filtered |> distinct(condition))
```

No effect of condition on meat inclusion.

<!-- Seems like a higher proportion of respondents are eating meat in intervention than control. -->

### By condition

```{r}
# contrasts(survey_long$condition) <- contr.sum

model_fun <- \(d) lm(value ~ condition, data = d)
coef_fun <- \(m) tidy(m, conf.int = TRUE) |> mutate(p.value = sprintf("%.2f", round(p.value, 2)))
fits_fun <- \(m) augment(m, se_fit = TRUE, interval = "confidence",
                         newdata = survey_long |> distinct(condition))

survey_fits <- survey_long |>
  nest(data = -measure) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun))
```

Differences by condition (condition is treatment coded):
```{r}
survey_fits |> select(measure, coefs) |> unnest(coefs)
survey_fits |> select(measure, fits) |> unnest(fits)
```

```{r, echo=FALSE}
# hunger_fits <- survey_fits |>
#   select(measure, fits) |>
#   unnest(fits) |>
#   filter(measure == "hunger")
# hungers <- set_names(hunger_fits$.fitted, hunger_fits$condition)
# hunger_increase <- hungers[["intervention"]] - hungers[["control"]]
# hunger_increase <- hungers[["intervention"]] - hungers[["control"]] / hungers[["control"]]
```

No effect of condition on any of satisfaction, hunger, and fullness.

Plot responses by condition with CIs from above models:
```{r, fig.width=8, fig.height=4.5}
fits <- survey_fits |> select(measure, fits) |> unnest(fits)
ggplot(survey_long, aes(x = condition, y = value, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                data = fits) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

### By condition and meat type

Differences by condition and meat type (both are effects coded):
```{r}
type_cells <- survey_long |> distinct(meat_target, condition)
model_fun_type <- \(d) lm(value ~ condition * meat_target, data = d)
fits_fun_type <- \(m) augment(m, se_fit = TRUE, interval = "confidence",
                              newdata = type_cells)

contrasts(survey_long$condition) <- contr.sum
contrasts(survey_long$meat_target) <- contr.sum
survey_fits_type <- survey_long |>
  filter(!is.na(meat_target)) |>
  nest(data = -measure) |>
  mutate(model = map(data, model_fun_type),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun_type))

survey_fits_type |> select(measure, coefs) |> unnest(coefs)
survey_fits_type |> select(measure, fits) |> unnest(fits) |> arrange(measure, meat_target, condition)
```

Controlled for meat type, no effect of condition on fullness.

Possible effect of condition on hunger (higher hunger in intervention). Not significantly different between meat types.

Possible effect of condition and meat type on satisfaction (satisfaction is higher in intervention for pork and beef but lower for chicken).

```{r, fig.width=10, fig.height=4.5}
fits_type <- survey_fits_type |> select(measure, fits) |> unnest(fits)
ggplot(survey_long, aes(x = condition, y = value, color = condition)) +
  facet_nested(~ measure + meat_target) +
  # facet_wrap(vars(measure, meat_target), nrow = 1) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                data = fits_type) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

### By condition, meat type, and meat inclusion

Differences by condition and meat type (both are effects coded), split up by whether meat was included.
```{r}
# contrasts(survey_long$condition) <- contr.treatment
survey_fits_meat <- survey_long |>
  nest(data = -c(measure, meat_inclusion)) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun)) |>
  mutate(model_type = map(data, model_fun_type),
         coefs_type = map(model_type, coef_fun),
         fits_type = map(model_type, fits_fun_type))
```

Differences by condition, split by whether meat was included:
```{r}
survey_fits_meat |>
  select(measure, meat_inclusion, coefs) |>
  unnest(coefs)

survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits)
```

No effects for satisfaction or fullness for both groups.

```{r, echo=FALSE}
hunger_fits_meat <- survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits) |>
  filter(measure == "hunger", meat_inclusion)
hungers_meat <- set_names(hunger_fits_meat$.fitted, hunger_fits_meat$condition)
hunger_increase_meat <- hungers_meat[["intervention"]] - hungers_meat[["control"]]
# hunger_increase_meat <- hungers_meat[["intervention"]] - hungers_meat[["control"]] / hungers_meat[["control"]]
```

Hunger effect is coming from respondents who did not eat meat, they report `r hunger_increase_meat` scale points higher hunger in intervention that in control.

Differences by condition and meat type, split by whether meat was included:
```{r}
survey_fits_meat |>
  select(measure, meat_inclusion, coefs_type) |>
  unnest(coefs_type)

survey_fits_meat |>
  select(measure, meat_inclusion, fits_type) |>
  unnest(fits_type)
```

Satisfaction interaction no longer present when split by meat inclusion.

Hunger effect from respondents who did not eat meat is still present controlled for meat type, no significant differences in it by meat type.

Plot responses by condition and meat inclusion with CIs from above models:
```{r, fig.width=10, fig.height=8}
fits_meat <- survey_fits_meat |> select(measure, meat_inclusion, fits_type) |>
  unnest(fits_type) |>
  mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))
survey_long <- survey_long |>
  mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))

ggplot(survey_long, aes(x = condition, y = value, color = condition)) +
  facet_nested(meat_inclusion ~ measure + meat_target) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                position = position_dodge(),
                data = fits_meat) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```
