---
title: "SCOOPS survey data analysis"
output:
  html_document:
    highlight_downlit: yes
    theme: cosmo
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggthemes)
library(ggforce)
library(glue)
library(lubridate)
library(broom)
library(ggh4x)

options(digits = 2)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE,
                      echo = FALSE, cache = TRUE, rows.print = 25,
                      dev.args = list(png = list(type = "cairo")))
.font <- "Source Sans Pro"
theme_set(theme_bw(base_family = .font, base_size = 13))
theme_update(panel.grid = ggplot2::element_blank(),
             strip.background = ggplot2::element_blank(),
             legend.key = ggplot2::element_blank(),
             # panel.border = ggplot2::element_blank(),
             # axis.line = ggplot2::element_line(),
             strip.text = ggplot2::element_text(face = "bold"))
```

## Load and tidy data

```{r, echo=FALSE, eval=FALSE}
read_csv("private/SCOOPS_qualtrics_2022-12-05.csv") |>
  select(-IPAddress, -email, -LocationLatitude, -LocationLongitude) |>
  write_csv("data/SCOOPS_qualtrics_sanitized_2022-12-05.csv")
```

```{r}
survey_raw <- read_csv("data/SCOOPS_qualtrics_sanitized_2022-12-05.csv")

# code the condition of each day
start_date <- ymd("2022-10-03")
end_date <- ymd("2022-11-11")
conditions <- tibble(date = seq(start_date, end_date, by = "days")) |>
  filter(wday(date, week_start = 1) <= 5) |>
  mutate(condition = rep(c("control", "intervention"), each = 5, length.out = n()),
         condition = as_factor(condition),
         week = rep(1:6, each = 5, length.out = n()),
         stage = if_else(week <= 4, "main study", "self-serve"))

survey_tidy <- survey_raw |>
  slice(3:n()) |> # first two rows are qualtrics metadata
  filter(Finished == "True") |> # remove empty responses
  rename(recorded = RecordedDate) |> # keep relevant metadata cols
  select(matches("^[a-z]", ignore.case = FALSE)) |> # remove other metadata cols
  select(-feedback) |> # also remove
  rename(satisfaction = satisfaction_1, hunger = hunger_1, fullness = fullness_1) |> # sliders have funky column names
  mutate(across(c(satisfaction, hunger, fullness), as.integer)) |> # slider values are integers
  mutate(target = target == "Yes", meat_inclusion = meat_inclusion == "Yes") |> # yes/no values are true/false
  mutate(recorded = as_datetime(recorded), date = date(recorded),
         day = wday(date, label = TRUE), hour = hour(recorded),
         .after = recorded) |> # get useful components of datetime
  mutate(in_range = date >= start_date & date <= end_date &
         !(day %in% c("Sat", "Sun")) & hour >= 11 & hour <= 16) |> # code responses from outside of study range
  left_join(conditions) |> # code conditions
  mutate(id = 1:n()) |>
  select(condition, week, everything())
```

```{r}
# add in meat types from weight data
# weights_tidy <- read_rds("../data/weights_tidy.rds")
# day_meats <- weights_tidy |>
#   filter(meal == "lunch", !is.na(dish)) |>
#   distinct(monthday, station, dish) |>
#   mutate(station = fct_recode(station, target = "Cardinal Sage", other = "Core Menu"),
#          dish = str_to_lower(dish),
#          date = date(monthday)) |>
#   select(-monthday) |>
#   pivot_wider(names_from = station, values_from = dish, names_prefix = "meat_")
day_meats <- read_csv("data/day_meats.csv") |> select(date, meat_target)

survey <- survey_tidy |>
  left_join(day_meats, by = "date") |>
  mutate(across(where(is.character), as_factor))

survey_filtered <- survey |>
  filter(target, in_range) |>
  filter(stage == "main study") |>
  select(-target, -in_range)

# write_csv(survey_filtered, "data/SCOOPS_survey_filtered_2022-12-05.csv")

survey_long <- survey_filtered |>
  pivot_longer(c(satisfaction, hunger, fullness), names_to = "measure", values_to = "rating") |>
  mutate(measure = fct_rev(measure))
```

## Response counts

Responses from outside of study range (before start, on weekend, or too late in the day): `r survey |> filter(!in_range) |> nrow()`

Responses from not eating at Cardinal Sage: `r survey |> filter(!target) |> nrow()`

Remaining responses: `r survey |> filter(target, in_range) |> nrow()`

Number of responses from each week/condition:
```{r}
survey_filtered |> count(week, condition)
survey_filtered |> count(condition)
```

## Demographic breakdown

Diet information

```{r}
bind_rows(
  survey_filtered |> count(diet) |> rename(value = diet) |> mutate(category = "diet"),
  survey_filtered |> count(meat_freq) |> rename(value = meat_freq) |> mutate(category = "meat_freq"),
  survey_filtered |> count(fish_freq) |> rename(value = fish_freq) |> mutate(category = "fish_freq"),
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```

Demographic information

```{r}
bind_rows(
  survey_filtered |> count(stanford_status) |> rename(value = stanford_status) |> mutate(category = "stanford_status"),
  survey_filtered |> count(gender) |> rename(value = gender) |> mutate(category = "gender"),
  survey_filtered |> count(race) |> rename(value = race) |> mutate(category = "race")
) |>
  mutate(category = fct_inorder(category)) |>
  select(category, value, n) |>
  group_by(category) |>
  mutate(prop = n / sum(n)) |>
  arrange(category, desc(n)) |>
  ungroup()
```


## Plot responses

Plot values by week:

```{r weeks, fig.width=10, fig.height=4.5}
ggplot(survey_long, aes(x = week, y = rating, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  # stat_summary(fun.data = mean_cl_boot, geom = "crossbar") +
  stat_summary(fun = mean, geom = "crossbar") +
  scale_x_continuous(breaks = 1:6, labels = \(b) paste("Week", b)) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

Plot values by condition:

```{r conditions, fig.height=4.5}
ggplot(survey_long, aes(x = condition, y = rating, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  stat_summary(fun = mean, geom = "crossbar") +
  # stat_summary(fun.data = mean_cl_boot, geom = "crossbar") +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

## Models

### Meat inclusion independence check

Check if intervention is affecting whether meat was eaten:
```{r}
meat_inclusion_model <- lm(meat_inclusion ~ condition, data = survey_filtered)
summary(meat_inclusion_model)
augment(meat_inclusion_model, se_fit = TRUE, interval = "confidence",
        newdata = survey_filtered |> distinct(condition))
```

No effect of condition on meat inclusion.

<!-- Seems like a higher proportion of respondents are eating meat in intervention than control. -->

### By condition

```{r}
# contrasts(survey_long$condition) <- contr.sum

model_fun <- \(d) lm(rating ~ condition, data = d)
coef_fun <- \(m) tidy(m, conf.int = TRUE) |> mutate(p.value = sprintf("%.2f", round(p.value, 2)))
fits_fun <- \(m) augment(m, se_fit = TRUE, interval = "confidence",
                         newdata = survey_long |> distinct(condition))

survey_fits <- survey_long |>
  nest(data = -measure) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun))
model_list <- set_names(survey_fits$model, survey_fits$measure)
```

Differences by condition (condition is treatment coded):

__satisfaction__:
```{r}
summary(model_list$satisfaction)
```

__hunger__:
```{r}
summary(model_list$hunger)
```

__fullness__:
```{r}
summary(model_list$fullness)
```

__coefficients__:
```{r}
survey_fits |> select(measure, coefs) |> unnest(coefs)
```

__fits__:
```{r}
survey_fits |> select(measure, fits) |> unnest(fits)
```

No effect of condition on any of satisfaction, hunger, and fullness.

Plot responses by condition with CIs from above models:
```{r conditions-ci, fig.width=8, fig.height=4.5}
fits <- survey_fits |> select(measure, fits) |> unnest(fits)
ggplot(survey_long, aes(x = condition, y = rating, color = condition)) +
  facet_wrap(vars(measure)) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                data = fits) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

### By condition and meat type

Differences by condition and meat type (both are effects coded):
```{r}
type_cells <- survey_long |> distinct(meat_target, condition)
model_fun_type <- \(d) lm(rating ~ condition * meat_target, data = d)
fits_fun_type <- \(m) augment(m, se_fit = TRUE, interval = "confidence",
                              newdata = type_cells)

contrasts(survey_long$condition) <- contr.sum
contrasts(survey_long$meat_target) <- contr.sum
survey_fits_type <- survey_long |>
  filter(!is.na(meat_target)) |>
  nest(data = -measure) |>
  mutate(model = map(data, model_fun_type),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun_type))
model_list_type <- set_names(survey_fits_type$model, survey_fits_type$measure)
```

__satisfaction__:
```{r}
summary(model_list_type$satisfaction)
```

__hunger__:
```{r}
summary(model_list_type$hunger)
```

__fullness__:
```{r}
summary(model_list_type$fullness)
```

__coefficients__:
```{r}
survey_fits_type |> select(measure, coefs) |> unnest(coefs)
```

__fits__:
```{r}
survey_fits_type |> select(measure, fits) |> unnest(fits) |> arrange(measure, meat_target, condition)
```

Controlled for meat type, no effect of condition on any of satisfaction, hunger, and fullness.

```{r meat-type, fig.width=10, fig.height=9}
nester <- element_line(colour = "grey20", size = 0.4)
resecter <- unit(12, "points")
fits_type <- survey_fits_type |> select(measure, fits) |> unnest(fits)

ggplot(survey_long, aes(x = condition, y = rating, color = condition)) +
  facet_nested_wrap(vars(measure, meat_target), ncol = 6,
                    nest_line = nester, resect = resecter) +
  # facet_wrap(vars(measure, meat_target), nrow = 1) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                data = fits_type) +
  scale_colour_ptol() +
  labs(y = "Response") +
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.title.x = element_blank())
```

### By condition and meat inclusion

<!-- Differences by condition and meat type (both are effects coded), split up by whether meat was included. -->
```{r}
# contrasts(survey_long$condition) <- contr.treatment
survey_fits_meat <- survey_long |>
  nest(data = -c(measure, meat_inclusion)) |>
  mutate(model = map(data, model_fun),
         coefs = map(model, coef_fun),
         fits = map(model, fits_fun)) |>
  mutate(model_type = map(data, model_fun_type),
         coefs_type = map(model_type, coef_fun),
         fits_type = map(model_type, fits_fun_type))

# survey_long |>
#   group_by(measure, meat_inclusion, condition) |>
#   summarise(mean_rating = mean(rating), n = n())
```

Differences by condition, split by whether meat was included:

__coefficients__:
```{r}
survey_fits_meat |>
  select(measure, meat_inclusion, coefs) |>
  unnest(coefs)
```

__fits__:
```{r}
survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits)
```

No effects for satisfaction or fullness for both groups.

Might be an effect for hunger when including meat?

```{r, echo=FALSE}
hunger_fits_meat <- survey_fits_meat |>
  select(measure, meat_inclusion, fits) |>
  unnest(fits) |>
  filter(measure == "hunger", meat_inclusion)
hungers_meat <- set_names(hunger_fits_meat$.fitted, hunger_fits_meat$condition)
hunger_increase_meat <- hungers_meat[["intervention"]] - hungers_meat[["control"]]
# hunger_increase_meat <- hungers_meat[["intervention"]] - hungers_meat[["control"]] / hungers_meat[["control"]]
```

__hunger measure when meat was included__:
```{r}
survey_fits_meat |> filter(meat_inclusion, measure == "hunger") |> pull(model) |> pluck(1) |> summary()
```

Respondents who ate meat responded `r hunger_increase_meat` scale points higher in intervention that in control.

```{r meat-inclusion, fig.width=10, fig.height=4.5}
fits_meat <- survey_fits_meat |> select(measure, meat_inclusion, fits) |>
  unnest(fits) |>
  mutate(meat_inclusion = if_else(meat_inclusion, "ate meat", "did not eat meat"))
survey_long <- survey_long |>
  mutate(meat_inclusion = if_else(meat_inclusion, "ate meat", "did not eat meat"))

ns <- survey_long |> count(measure, condition, meat_inclusion) |>
  mutate(n = glue("n = {n}"))
  
ggplot(survey_long, aes(x = condition, y = rating, color = condition)) +
  coord_cartesian(clip = "off") +
  facet_nested_wrap(c(vars(measure), vars(meat_inclusion)), nrow = 1,
                    nest_line = nester, resect = resecter) +
  geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.5) +
  geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
                # position = position_dodge(),
                data = fits_meat) +
  geom_text(aes(label = n), y = 105, family = .font, size = 2, colour = "grey20", data = ns) +
  scale_colour_ptol(guide = "none") +
  labs(y = "Response", caption = "Figure 4: Survey respondents' ratings of their satisfaction (left), hunger (middle), and fullness (right), separated by whether they ate meat in the meal\n(boxes indicate means and 95% confidence intervals).") +
  theme(axis.title.x = element_blank(),
        plot.caption = element_text(hjust = 0, size = rel(0.85)),
        plot.caption.position = "plot")

ggsave("plots/survey_conditions.png", width = 8.5, height = 4)
```

<!-- Differences by condition and meat type, split by whether meat was included: -->
```{r}
# survey_fits_meat |>
#   select(measure, meat_inclusion, coefs_type) |>
#   unnest(coefs_type)
# 
# survey_fits_meat |>
#   select(measure, meat_inclusion, fits_type) |>
#   unnest(fits_type)
```

<!-- Plot responses by condition and meat inclusion with CIs from above models: -->
```{r, fig.width=10, fig.height=8}
# fits_meat <- survey_fits_meat |> select(measure, meat_inclusion, fits_type) |>
#   unnest(fits_type) |>
#   mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))
# survey_long <- survey_long |>
#   mutate(meat_inclusion = if_else(meat_inclusion, "yes meat", "no meat"))
# 
# ggplot(survey_long, aes(x = condition, y = rating, color = condition)) +
#   facet_nested(meat_inclusion ~ measure + meat_target) +
#   geom_sina(aes(group = date), size = 0.6, alpha = 0.6, maxwidth = 0.6) +
#   geom_crossbar(aes(y = .fitted, ymin = .lower, ymax = .upper), width = 0.8,
#                 position = position_dodge(),
#                 data = fits_meat) +
#   scale_colour_ptol() +
#   labs(y = "Response") +
#   theme(legend.position = "bottom", legend.title = element_blank(),
#         axis.title.x = element_blank())
```

## Exploratory stuff

__demographic covariates__

```{r demographic, fig.width=10}
demo_long <- survey_long |>
  # filter(!str_detect(gender, "Prefer not")) |>
  mutate(meat_freq = fct_relevel(meat_freq, "0", "1-7", "8-14", "15-21", "22+"),
         fish_freq = fct_relevel(meat_freq, "0", "1-7", "8-14", "15-21", "22+"),
         diet = fct_relevel(diet, "Meat", "Flexitarian", "Pescatarian", "Vegetarian", "Vegan"),
         gender = fct_lump_n(gender, 2),
         meat_freq = fct_collapse(meat_freq, "15+" = c("15-21", "22+")),
         fish_freq = fct_collapse(fish_freq, "15+" = c("15-21", "22+")),
         diet = fct_collapse(diet, "Pescatarian/Vegetarian/Vegan" = c("Pescatarian", "Vegetarian", "Vegan"))) |>
         # meat_freq = fct_lump_prop(meat_freq, 0.01)) |>
         # diet = fct_lump_prop()) |>
         # gender = fct_collapse(gender, "Non-binary/Other" = c("Non-binary", "Other")) |> fct_infreq()) |>
  pivot_longer(c(meat_freq, fish_freq, diet, gender), names_to = "demo", values_to = "demo_value") |>
  mutate(demo = fct_relevel(demo, "gender"))
  
demo_long |> count(measure, demo, demo_value) |> filter(measure == "satisfaction")
ggplot(demo_long |> filter(measure == "satisfaction"),
       aes(x = demo_value, y = rating, colour = condition)) +
  # facet_grid(vars(measure), vars(demo), scales = "free", space = "free") +
  # facet_grid(rows = vars(demo), scales = "free", space = "free") +
  facet_wrap(vars(demo), nrow = 1, scales = "free_x") +
  # geom_point()
  # geom_sina(aes(group = condition)) +
  stat_summary(fun.data = mean_cl_normal, position = position_dodge(width = 0.4)) +
  # stat_summary(geom = "text", fun = length) +
  scale_colour_ptol(name = "") +
  scale_y_continuous(breaks = seq(0, 100, 10), name = "Hunger rating") +
  theme(axis.title.x = element_blank(),
        legend.position = "bottom")
```

```{r, eval = FALSE}
contrasts(survey_long$diet) <- contr.sum
contrasts(survey_long$meat_freq) <- contr.sum
contrasts(survey_long$fish_freq) <- contr.sum
contrasts(survey_long$stanford_status) <- contr.sum
contrasts(survey_long$gender) <- contr.sum
contrasts(survey_long$race) <- contr.sum

sat <- survey_long |> filter(measure == "satisfaction")
  # mutate(meat_inclusion = factor(meat_inclusion))
# contrasts(sat$meat_inclusion) <- contr.sum

lm(rating ~ condition + diet, data = sat) |> summary()
lm(rating ~ condition * diet, data = sat) |> summary()
lm(rating ~ condition + meat_freq, data = sat) |> summary()
lm(rating ~ condition + fish_freq, data = sat) |> summary()
lm(rating ~ condition + stanford_status, data = sat) |> summary()
lm(rating ~ condition + gender, data = sat) |> summary()
lm(rating ~ condition + race, data = sat) |> summary()
```

__temporal trends__

```{r temporal, fig.width=10}
ggplot(survey_long, aes(x = date, y = rating)) +
  facet_wrap(vars(measure)) +
  geom_point() +
  # geom_sina(aes(group = date))
  geom_smooth(method = "lm")
```

__day effects__

```{r wday, fig.width=10}
ggplot(survey_long, aes(x = wday(date), y = rating)) +
  facet_wrap(vars(measure)) +
  # geom_point() +
  geom_sina(aes(group = wday(date))) +
  geom_smooth(method = "lm")
```
